\documentclass{article}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage[linewidth=1pt]{mdframed}
\usepackage[colorlinks]{hyperref}

\usepackage{verbatim}

\usepackage{algorithm}
\usepackage{algpseudocode}

\hypersetup{citecolor=DeepPink4}
\hypersetup{linkcolor=DarkRed}
\hypersetup{urlcolor=Blue}

\usepackage{cleveref}

\setlength{\parindent}{1em}
\setlength{\parskip}{1em}
\renewcommand{\baselinestretch}{1.0}

\begin{document}

\begin{titlepage}
	\centering
	{\scshape\LARGE Assignment 4\par}
	\vspace{1cm}
	{\scshape\Large Algorithms \& Complexity (CIS 522-01)\par}
	\vspace{1.5cm}
	{\Large\itshape Javier Arechalde\par}
	\vfill
	{\large \today\par}
\end{titlepage}

\section*{Part A: Read the solved exercises and Practice}

\subsection*{Solved excercise \#1 in Chapter 5}

In this problem, we have an array with $n$ entries, and inside this array, we have a peak entry $p$ in a position $j$ of the array, so that the values in the array prior to $j$ go in increasing order, and after the peak value, they go in decreasing order.

Our goal is to find that peak entry $p$ without having to read the entire array, and only by reading as few values as possible. 

\subsubsection*{Algorithm Pseudocode}

\begin{algorithm}[H]
\caption{Finding maximum pseudocode}
\begin{algorithmic}[1]
\Function{Findmaximum}{$pos_{start},pos_{end},array$}
 \State $n = (pos_{start}+pos_{end})/(2)$
 \If{$array(\frac{n}{2}-1)<array(\frac{n}{2})<array(\frac{n}{2}+1)$}
  \State We have a \textbf{positive slope}, so we havent reached the maximum yet
  \State \Call{Findmaximum}{$(pos_{start}+pos_{end})/2, pos_{end}, array$}
 \ElsIf{$array(\frac{n}{2}-1)>array(\frac{n}{2})>array(\frac{n}{2}+1)$}
  \State We have a \textbf{negative slope}, we already passed the maximum
  \State \Call{Findmaximum}{$pos_{start},(pos_{start}+pos_{end})/2$}
 \ElsIf{$array(\frac{n}{2}-1)>array(n/2)<array(\frac{n}{2}+1)$}
  \State We have found the \textbf{maximum point}
  \State \Return value(n/2)
 \EndIf
\EndFunction
\end{algorithmic}
\end{algorithm}

\subsubsection*{Solution for problem instance of size $10$}

In this case, we will run our algorithm, when we have an instance of size $10$.

In this problem's scope, we will have an set of increasing numbers that grow until a maximum, followed by another set of numbers that go in decreasing order.

This will be our problem's working set:

$$S = [1,2,4,12,14,21,6,4,3,1]$$

If we start running the algorithm, we will check the number in the $5^{th}$ position.

In this case we will have that $S[4]<S[5]<S[6]$, which means that we are in a positive slope, and we still haven't reached the maximum. Then we will call the function again, so in the next iteration of our algorithm, we will work with this set.

$$S' = [14,21,6,4,3,1]$$

Now we will check the $3^{rd}$ position. In this case we have that $S[2]>S[3]>S[4]$, which means that we are in a negative slope, so we already passed the maximum. Thus, we will call the function again, and in the next iteration of our algorithm we will work with this set.

$$S'' = [14,21,6]$$

Now we will check the middle position, in this case the $2^{nd}$ position. We get the result that $S[1]<S[2]>S[3]$, which means that the number we are checking is indeed the maximum. Now we will return that value, and stop running our algorithm.

$$max = 21$$

\subsubsection*{Time Complexity}

In this problem, with each one of the recursive calls, we reduce the problem to one of at most half the size of the initial problem. Then:

$$T(n)\leq T(n/2) + c$$

when $n>2$, and

$$T(2)\leq c.$$

Then, the running time of our algorithm will be $O(\log n)$.

\subsection*{Solved exercise \#2 in Chapter 5}

In this problem, we have an investment company that looks at $n$ consecutive days of a given stock. For each of these days, the stock has a price $p(i)$ per share for the stock on that day. We assume that the stock prize was fixed on that day.

The goal is to find, without having to check each possible combination of days, which will take $O(n^2)$, in which day they should have bought the shares, and in which day they must have sold them to make as much money as possible.

\subsubsection*{Algorithm Pseudocode}

\begin{algorithm}[H]
\caption{Stocks Divide-and-Conquer pseudocode}
\begin{algorithmic}[1]
\Function{Max}{list}
 \State $max$
 \For{element in list}
  \If{$element>max \quad \textbf{or} \quad max == NA$}
   \State max = element
  \Else{}
   \State \textbf{continue}
  \EndIf
 \EndFor
 \State \Return max
\EndFunction
\State
\Function{Min}{list}
 \State $min$
 \For{element in list}
  \If{$element<min \quad \textbf{or} \quad min == NA$}
   \State min = element
  \Else{}
   \State \textbf{continue}
  \EndIf
 \EndFor
 \State \Return min
\EndFunction
\State
\Function{FindOpt}{$array$}
\If{$len(array)>2$}
 \State $Larray = array[0:len(array)/2]$
 \State $Rarray = array[len(array)/2:len(array)]$
 \State
 \State LSide = \Call{FindOpt}{$Larray$}
 \State RSide = \Call{FindOpt}{$Rarray$}
 \State
 \State LOpt = LSide[1] - LSide[0]
 \State ROpt = RSide[1] - RSide[0]
 \State MOpt = \Call{Max}{RSide} - \Call{Min}{LSide}
 \State
 \State Marray = [min(LSide),max(RSide)]
 \State
 \State maxvalue = \Call{Max}{LOpt,ROpt,MOpt}

 \If {$maxvalue == LOpt$}
  \State \Return LSide
 \ElsIf{$maxvalue == ROpt$}
  \State \Return RSide
 \ElsIf{$maxvalue == MOpt$}
  \State \Return Marray
 \EndIf
 \State
\ElsIf{$len(array) <= 2$}
 \State \Return array
\EndIf
\EndFunction
\end{algorithmic}
\end{algorithm}

\subsubsection*{Solution for problem instance of size $10$}

Now we will compute a solution using our algorithm for a problem instance of size 10.

This will be the set we are going to work with.

$$S = [7,4,3,2,5,7,10,20,14,7]$$

First, as the array is longer than 2, we will divide it into two sets recursively until we have arrays of length smaller or equal to 2.

$$[7,4,3,2,5] \quad [7,10,20,14,7]$$

$$[7,4] \quad [3,2,5] \quad [7,10] \quad [20,14,7]$$

$$[7,4] \quad [3,2] \quad [5] \quad [7,10] \quad [20,14] \quad [7]$$

Now we are going to compare set by set, if the optimal solution between one set, compare it with the other set, and compare it also with the maximum of the "right" set and the minimum of the "left" set, and see which one gives us a better solution.

$$[7,4] \quad \& \quad [3,2]$$

$$OptL = 4-7 = -3 \quad OptR = 2-3 = -1 \quad OptM = 3-4 = -1$$

$$[5] \quad \& \quad [7,10]$$

$$OptM = 10-5 = 5 \quad OptR = 3$$

$$[20,14] \quad  \& \quad [7]$$

$$OptL = -6 \quad OptM = 7-14 = -7$$

We return $[3,2] \quad [5,10] \quad [20,14]$.

Now we have:

$$[3,2] \quad [5,10] \quad [20,14]$$

Lets start comparing.

$$[3,2] \quad \& \quad [5,10]$$

$$OptL = -1 \quad OptR = 5 \quad OptM = 10 - 2 = 8$$

We return $[2,10]$.

Now we have:

$$[2,10] \quad \& \quad [20,14]$$

$$OptL = 8 \quad OptR = -6 \quad OptM = 18$$

We finally return $[2,20]$, and that will be our final result.

\subsubsection*{Time Complexity}

As we said, in this problem, we will have to recursively subdivide our array, and take the best possible solution out of this three possible solutions:

\begin{itemize}
 \item The optimal solution on $S$
 \item The optimal solution on $S'$
 \item the optimal solution of $p(j)-p(i)$, over $i \in S$ and $j \in S'$.
\end{itemize}

The first two items are computed, in time $T(n/2)$ by recursion, and the third item is computed by finding the maximum in $S'$ and the minimum in $S$, which can be done in $O(n)$ time. Then our running time $T(n)$ satisfies

$$T(n) \leq 2T(\frac{n}{2})+O(n)$$,

Then the time complexity of our implementation will be $O(n\log n)$.


\section*{Part B: Problem Solving}

\subsection*{Significant inversion}

\subsubsection*{Problem Model}

In this problem, we are given a sequence of $n$ numbers $a_1,...,a_n$, which we will we assume that are all distinct, and we define inversion to be a pair $i<j$ such that $a_i>a_j$. We call a pair \textit{significant inversion} if $i<j$ and $a_i<2a_j$.

Our goal is to count the number of \textit{significant inversions} between two orderings, using an algorithm that has $O(n \log n)$ time complexity.

We also added some improvements to the pseudocode. If for example, while we are merging the two sorted arrays, we finish adding elements from one array while there are still elements available in the other array, we will add this remaining elements and exit the while loop.

\subsubsection*{Pseudocode}

\begin{algorithm}[H]
\caption{Significant inversion pseudocode}
\begin{algorithmic}[1]
\Function{CountInversions}{array}
 \If{$length(array)>2$}
  \State Divide the array in two halves $array_{left}$ and $array_{right}$ and
  \State recursively call this function
  \State $array_{left} = \Call{CountInversions}{array_{left}}$
  \State $array_{right} = \Call{CountInversions}{array_{right}}$
  \While{We havent sorted $array_{left}$ and $array_{right}$}
   \State $value_{left}  = array_{left}[i]$ and $value_{right} = array_{right}[k]$
   \If{We added all the elements in $array_{left}$}
    \State $array_{sorted} = array_{sorted} + array_{right}[j:end]$
    \State Break loop
   \ElsIf{We added all the elements in $array_{right}$}
    \State $array_{sorted} = array_{sorted} + array_{left}[i:end]$
    \State Break loop
   \EndIf
   \If{$value_{left}<value_{right}$}
    \State Add $value_{left}$ to the end of$array_{sorted}$
    \State i++
   \Else
    \State Add $value_{right}$ to the end of$array_{sorted}$
    \State j++
    \If{$value_{left}>2*value_{right}$}
     \State All the elements from position $i$ to the end will be greater
     \State too as $array_{left}$ is sorted in increasing order
     \State $N_{inv} = N_{inv} + length(array_{left}) - i$
    \EndIf
   \EndIf
  \EndWhile
  \State \Return $array_{sorted}$
 \EndIf
 \If{$length(array) == 1$}
  \State \Return array
 \ElsIf
  \If{$array[0]<array[1]$}
   \State \Return $array[0],array[1]$
  \Else
   \If{$array[0]>2*array[1]$}
    \State $N_{inv}++$
   \EndIf
   \State \Return $array[1],array[0]$
  \EndIf
 \EndIf
\EndFunction
\end{algorithmic}
\end{algorithm}

\subsubsection*{Implementation}

Here is the code for the implementation of the \textit{pseudocode} shown above.

\lstinputlisting[language=Python]{Problem52.py}

\subsubsection*{Running time}

Our algorithm uses mergesort to sort the array and count the number of significant inversions at the same time, so the running time of our algorithm will be $O(n\log n)$

\subsection*{Local minimum}

\subsubsection*{Problem Model}

In this problem, we are give a complete binary tree $T$. They also state that the number of nodes is $n = 2^d -1$ for some $d$, which means that the tree is not only complete, but is also perfect, which means that all nodes that have childre, have two children, and all leaves are at the same level. This is extremely important, as if the tree was only complete, instead of perfect, we wont have all the leaves at the same level, so we would have to come up with a method to avoid trying to go deeper into the tree when we were reaching the last level, which is not completely filled and all the leaves are as left as possible.


Each node $v$ of $T$ is labeled with a real number $x_v$. For each node in the tree, we can only determine its value $x_v$ by probing the node $v$.

Our goal is to find a local minimum, that is if the label $x_v$ is less than the label $x_w$ for all the nodes $w$ that are joined to $v$ by an edge.  We also have to find this local minimum of $T$ using only $O(log n)$ probes to the nodes of $T$.

In our proposal, we will recursively go deeper into the tree until we reach the leave nodes, once we reach the leave nodes, we will compare the one on the left and the one on the right and return the smaller one, while we go up until the tree root node.

To explore the tree, we will use a position array called $pos_{array}$ that we will initialize as $\{0\}$ and when we go deeper in the tree, we will append in each level, a $0$ if we are exploring the left branch and $1$ if we are exploring the right branch. Then when we want to probe a node, we will use this array to reference it. For example, if the tree has $d = 3$ and we want to reference the leftmost leave, we will do $x_{v} = T(\{0,0,0\})$

\subsubsection*{Pseudocode}

\begin{algorithm}[H]
\caption{Local minimum pseudocode}
\begin{algorithmic}[1]
\Function{FindMin}{$T,level,pos_{array}$}
 \If{We havent reached the leaves of T}
  \State We go down one level in the tree
  \State $left_val = \Call{FindMin}{Tree,level+1,pos_{array}.append(0)}$
  \State $right_val = \Call{FindMin}{Tree,level+1,pos_{array}.append(1)}$
  \State
  \State We find the minimum value and return it
  \If{$left_{val}<right_{val}$}
   \State \Return $left_{val}$
  \Else
   \State \Return $right_{val}$
  \EndIf
 \EndIf

 \If{We are on a leaf}
  \State \Return $x_v$
 \EndIf
\EndFunction
\end{algorithmic}
\end{algorithm}

\subsubsection*{Running time}

\end{document}